External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-12 CVPR2017_Review_Unified.tex
add

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.85\linewidth]{Flowchart3.png}
\vspace{-2mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

\begin{figure*}\vspace{-1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (b) External: 39.05dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (c) Internal: 38.75dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (d) Guided Internal: \textbf{39.39}dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (e) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig4}
\end{figure*}
\begin{figure*}\vspace{-1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering  
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.02dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth} 
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (b) External: 35.58dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (c) Internal: 36.74dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (d) Guided Internal: \textbf{37.87}dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (e) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the $111$-th cropped image from ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\vspace{-2mm}
\label{fig5}
\end{figure*}

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\begin{small}
\vspace{-1mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{39.57}  & 667.36 & 41.89
\\
\hline
\end{tabular}
\end{center}\vspace{-4mm}
\end{small}
\end{table}

>>>>

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.8\linewidth]{Flowchart3.png}
\vspace{-2mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

\begin{figure*}\vspace{-1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (b) External: 39.05dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (c) Internal: 38.75dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (d) Guided Internal: \textbf{39.39}dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (e) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\vspace{-1mm}
\label{fig4}
\end{figure*}
\begin{figure*}\vspace{-1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering  
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.77dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth} 
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
{\footnotesize (b) External: 36.97dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
{\footnotesize (c) Internal: 37.40dB }
\end{minipage} 
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
{\footnotesize (d) Guided Internal: \textbf{38.01}dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
{\footnotesize (e) Mean Image \cite{crosschannel2016}}
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the $111$-th cropped image from ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\vspace{-2mm}
\label{fig5}
\end{figure*}

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\begin{small}
\vspace{-1mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{39.57}  & 587.36 & 41.89
\\
\hline
\end{tabular}
\end{center}\vspace{-4mm}
\end{small}
\end{table}
